Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-19 final_metrics_analysis.Rmd
Attempted mosaic plot of recidivism by race - caucasian not showing up

@@

```{python exploratory race bar plot}
# barplot of race
sns.countplot(x="race", data=df_viz, palette=workshop_palette)
plt.title('Race Distribution (White and Black individuals only)')
```

>>>>

```{python crosstable of recitivism by race}
crosstable=pd.crosstab(df_viz['race'],df_viz['two_year_recid'])
crosstable
```

```{python exploratory recidivism mosaic plot}
props={}
props[('Caucasian','Recidivated')]={'facecolor':'red', 'edgecolor':'white'}
props[('Caucasian','Survived')]={'facecolor':'red', 'edgecolor':'white'}
props[('African-American','Recidivated')]={'facecolor':'xkcd:aqua','edgecolor':'white'}
props[('African-American','Survived')]=        {'facecolor':'xkcd:aqua','edgecolor':'white'}
labelizer=lambda k:{('Caucasian','Recidivated'):1242,('African-American','Recidivated'):1661,('Caucasian','Survived'):858,('African-American','Survived'):1512}[k]
mosaic(df_viz,['race','two_year_recid'],labelizer=labelizer,properties=props)
plt.show()
```

@@

```{python exploratory race bar plot}
# barplot of race
sns.countplot(x="race", data=df_viz, palette=workshop_palette)
plt.title('Race Distribution (White and Black individuals only)')
plt.show()
```
